The Soulgem Paper

### 2011-09-22 soulgem.tex
First draft of Findings complete.

% On media

% People enacting different (but connected) roles communicate through boundary objects. Within roles, however, the communication media could be different. Since (a) communication media vary across roles, and (b) most or many roles are essential to the functioning of the organization and the satisfaction of its goals, studying/mining a single medium will miss important people and interactions.

@@

@@

@@

% Brief summary of findings and implications.

>>>>

We expected to find that people enacting similar roles would use similar communication media, and that they would communicate with people enacting interfacing roles through other media. Although we found support for this claim, as we explain below, a biasing factor was the prevalence of face-to-face interactions in both of our field sites. Face-to-face was widely used in communication between people with similar and with different roles. Stand-up meetings, walks across the hall, and group meetings were commonplace.

Regarding other media, we found role-based differences in medium selection and use. The broadest medium---the one that had the greatest use among the most kinds of roles---was the issue tracking system. People with expectations regarding code production, quality assurance, customer service, field implementation, product management, and performance monitoring all used the issue tracking system to some extent. Its use was not uniform: some group members used it to emit messages, others were mostly listeners, and others were more interested in the aggregate than in the contents of particular electronic traces.

% TODO: Check if this is matches deSouza and Redmiles' observations.

The use of other media was more localized. In Gallium, IRC use was common among some developer teams, while Customer Support used Google Documents to keep track of some of its cases. Email and phone were more heavily used in the management side of the organization than on its technical core.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Implications}

@@

\subsection{Threats to Validity}

@@

% Very brief summary of findings and implications.
